Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-18 ms.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:result}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The stellar wind density, $n$ in equation (\ref{eq:Pinp_kin}) is estimated by
%%%
\begin{equation}
n = \frac{\dot M}{4\pi a^2 m_p v}
\end{equation}
%%%
where $\dot M$ is the mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass. 
The mass loss rate of red giants are typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{How?}. The rate can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\dot M_{\odot } \sim 10^{-14} M_{\odot}$/yr. 
Therefore, we have
%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
\begin{equation}
\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
\end{equation}

On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to expanded stellar radius)\footnote{Escape velocity is $\sqrt{2GM/r}$.}. Assuming that the stellar wind scales as the escape velocity, RGs with radius $R=100R_{\odot}$ have 10 times as slow stellar wind as that at the main sequence. \memoYF{Estimate in more detail?}
\begin{equation}
\frac{v}{v_{\odot}} \sim 10^{-1}
\end{equation}

The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}. 
\begin{equation}
\frac{T}{T_{\odot}} \sim 10^{-2}
\end{equation}

In order to estimate the planetary magnetic field of general planets, we adopt simple scaling relation between the magnetic field and planetary properties. 
Several relationships have been proposed so far by \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary).

They are compared with numerical simulations in \citep{christensen2010}. We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007, spiegel+burrows2012}.
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

The convected heat flux $q_c$ is estimated from the numerical simulation of \citep[e.g.][]{burrows_et_al2001,marley2007}. 
According to \citet{burrows_et_al2001}, the luminosity scale with time as
%%%%%%%%%%
\begin{equation}
L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
\memoYF{Burrows et al. 2001 implies $10^{-9} L_\odot $, but looks to me like it is actually $10^{-8} L_\odot $}. 
We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.

There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
%
Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 
\memoYF{Would their spin rate become higher or lower??}
\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}

>>>>>>> c540a35c06ae4ad467ac103fe5b2e2b7605650a9
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:result}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
